\documentclass[lighthipster]{simplehipstercv}
    % available options are: darkhipster, lighthipster, pastel, allblack, grey, verylight, withoutsidebar
    % withoutsidebar
    \usepackage[utf8]{inputenc}
    \usepackage[default]{raleway}
    \usepackage[top=3cm, bottom=1cm, left=2cm, right=2cm, a4paper]{geometry}
    \usepackage{xcolor}
    \hypersetup{
        colorlinks,
        linkcolor={red!50!black},
        citecolor={blue!50!black},
        urlcolor={blue!80!black}
    }
    \title{CV}
    \author{\LaTeX{} Ninja}
    \date{2024}
    \pagestyle{empty}
    \begin{document}
    
    
    \thispagestyle{empty}
    \simpleheader{headercolour}{David}{Brockbank}{Software Engineer}{white}
    \vspace{5em}
    \small
    
    \begin{minipage}[t]{1\textwidth}
    \section*{About}
    Graduate software engineer with a year professional experience in the software development industry.\\
    Enjoyer of collaborative problem solving, experienced in Java, C\#, Javascript, React, Python, and SQL.\\
    Projects done with C, C++, Python, and Java. CAD and electronic hobbyist.
    \end{minipage}    
    \bigskip

    \begin{minipage}[t]{1\textwidth}
    \section*{Experience}
    
    \textbf{Software Implementation Consultant}\\
    \textbf{Fast Enterprises }\textbullet{ Full-time}\\
    Nov 2023 - Jun 2024 \textbullet{ 8 mos}\\
    Development and consulting for Inland Revenue's tax software. 
        Worked with non-technical client to discuss issues and requirements. 
        Implemented features and fixes in C\#, .NET, and SQL, worked closely with domain specialists to extensively test before releasing to production.
        Evaluated potential features against system capabilities and clearly communicated them to the client. \\
    
    \textbf{Software Engineer Intern}\\
    \textbf{MTF Finance }\textbullet{ Internship}\\
    Sep 2023 - Nov 2023 \textbullet{ 3 mos}\\
    Researched potential technologies to be used for an upgrade of internal lending software.
                Used C\#, .NET, and SQL for main technology stack but researched Python, Django, and Vue.\\
    
    \textbf{Computer Science Demonstrator}\\
    \textbf{University of Otago }\textbullet{ Part-time}\\
    Feb 2023 - Jun 2023 \textbullet{ 5 mos}\\
    Guided students completing lab work for COSC202 - Software Development. Most of the work was in Java.\\
    
    \textbf{Software developer}\\
    \textbf{Iris Data Science }\textbullet{ Internship}\\
    Dec 2022 - Mar 2023 \textbullet{ 4 mos}\\
    Design and development on a agricultural farming PWA for Agriganics in Javascript, React, and SQL. 
        Implemented extensive offline capabilities, workflow design, and front-end development. 
        Focus on defining, creating, and refining user experience on mobile and desktop environments.\\
    
    \textbf{Digital Archiver}\\
    \textbf{Thames Treasury }\textbullet{ Volunteer}\\
    Aug 2020 - Oct 2020 \textbullet{ 3 mos}\\
    Digitized historical records and photographs relevant to the Thames-Coromandel area.\\
    
    \textbf{Plasterer, Labourer}\\
    \textbf{S \& M Property Management Limited }\textbullet{ Casual}\\
    Nov 2016 - Dec 2022 \textbullet{ 6 yrs, 2 mos}\\
    Installing electric fencing, building frames, concrete pouring, painting, and plastering. Occasional leadings of small teams. Full-time during summers, part-time during school.\\
      
    \end{minipage}    
    \bigskip
    
    \begin{minipage}[t]{1\textwidth}
    \section*{Education}
    
    \textbf{Bachelor of Science}\\
    \textbf{University of Otago}\\
    Major in Computer Science, Minor in Energy Management\\
    GPA: 8.3/9.0 (A)\\
    
    \end{minipage}
    \bigskip
    
    \begin{minipage}[t]{1\textwidth}
    \section*{Awards}
    Stephen Bowater Memorial Scholarship\\
    University of Otago 150th Entrance Scholarship\\
    University of Otago Scholarship in Science
    \bigskip
    \bigskip
    
    \end{minipage}\hfill
\setlength{\parindent}{0pt}

\begin{minipage}[t]{1\textwidth}
\fontfamily{\sfdefault}\selectfont \color{black!70}
{\begin{center}\small 
    \href{mailto:davbrockbank@gmail.com}{\icon{\faEnvelopeO}{cvgreen}{} davbrockbank@gmail.com}  
    \href{tel:021493283}{\icon{\faPhone}{cvgreen}{} (+64) 21493283}  
 \end{center}
\begin{center}
    \href{https://davebroc.github.io/}{\icon{\faGlobe}{cvgreen}{}davebroc.github.io/}
    \href{https://www.linkedin.com/in/david-brockbank/}{\icon{\faLinkedin}{cvgreen}{}linkedin.com/in/david-brockbank/}
\end{center}
}
\end{minipage}

\end{document}


